Using Fundamental Measure Theory to Treat the Correlation Function of the Inhomogeneous Hard-Sphere Fluid

### 2012-08-30 papers/contact/paper.tex
yet a few more minor edits to contact paper Tests skipped!

Here we discuss the high-density results (filling fraction of 0.4),
which are shown in Figures~\ref{fig:walls-40}-\ref{fig:outer-40}.

Although the general density attributes look similar to those of the low density calculations as one moves away from the surfaces, the range of difference is altered.  The spikes at the surfaces reach a height of roughly five times the homogeneous average, whereas with the low densities the difference is closer to a factor of $0.5$.  With a higher density of spheres to pack in those that are up against the wall, it is more difficult for those spheres to ever find their way out and away.  We also notice that the downward trend in both $n_0$ and $n_A$ have similar characteristics but are over all much more flat.  (Don't see why!)

We once again see that in the $S$ case, although neither functionals
tested fit perfectly, Yu and Wu's functional is a closer fit than the
White Bear's.  We can see in the monte carlo's oscillations over
increased distance from the surfaces that there are layers of spheres
that are formed.  If one picks a point in one of these layers, that
point is more likely to be a contact point between spheres, whereas if
one picks a sphere a little over half a radius away, the likelyhood is
at a minimum.  There is then another maximum at roughly one radius
away from the surface.  (This suggests close packed layers?)

As with the lower densities, the $A$ case White Bear fits to the monte
carlo simulations very well.  The Gross functional seems to be
accurate until it falls off close to surfaces.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Conclusion}
We investigated several approximations to the contact value of the
correlation function for inhomogeneous fluid distributions
corresponding to flat walls, and both concave and convex walls.  We
defined and simulated two averages of the correlation function, an
asymmetric $A$ average centered at the location of one of the two
spheres that is in contact, and a symmetric $S$ average centered at
the point of contact of touching spheres.  For each average, we
derived a functional form from FMT, and also found an approximation
that has been used in the literature.  When compared with essentially
exact Monte Carlo simulations, the $A$ correlation function derived
from Fundamental Measure Theory in Section~\ref{sec:g-A} gives
excellent results for each surface, and at both high density and low
density.  The other three approximations that we studied all showed
significant and systematic deviations under some circumstances.  Thus,
we recommend that creators of SAFT-based classical density functionals
consider using the $g_\sigma^A$ functional defined in
Section~\ref{sec:g-A}.

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Conclusion}
We investigated several approximations to the contact value of the
correlation function for inhomogeneous fluid distributions
corresponding to flat, concave, and convex walls.  We
defined and simulated two averages of the correlation function, an
asymmetric $A$ average centered at the location of one of the two
spheres that is in contact, and a symmetric $S$ average centered at
the point of contact of touching spheres.  For each average, we
derived a functional form from FMT, and also found an approximation
that has been used in the literature.  When compared with essentially
exact Monte Carlo simulations, the $A$ correlation function derived
from Fundamental Measure Theory in Section~\ref{sec:g-A} gives
excellent results for each surface, at both high density and low
density.  The other three approximations that we studied all showed
significant and systematic deviations under some circumstances.  Thus,
we recommend that creators of SAFT-based classical density functionals
consider using the $g_\sigma^A$ functional defined in
Section~\ref{sec:g-A}.
